R Notebook

### 2022-04-06 R/DeaminationAnalysis.rmd
Update DeaminationAnalysis.rmd

# Extract tandem C>T mismatches

@@

>>>>

# Extract and simplify tandem C>T mismatches
CPDTandemCTMismatches = lapply(CPDMismatchData, function(x) lapply(
  x, function(y) simplifyTable(getTandemCTMismatches(y))
))
sixFourTandemCTMismatches = lapply(sixFourMismatchData, function(x) lapply(
  x, function(y) simplifyTable(getTandemCTMismatches(y))
))

@@

```{r plot_CPD_tandem_C>T_pos_frequency}
for (i in 1:length(CPDTandemCTMismatches)) {
  for (j in 1:length(CPDTandemCTMismatches[[i]])) {
    plotMismatchPositionFrequencies(CPDTandemCTMismatches[[i]][[j]],
                                    title = paste("CPD", names(CPDTandemCTMismatches)[i], 
                                                  names(CPDTandemCTMismatches[[i]])[j], "Tandem C>T Mismatch Pos"))
  }
}
```

```{r plot_6-4_tandem_C>T_pos_frequency}
for (i in 1:length(sixFourTandemCTMismatches)) {
  for (j in 1:length(sixFourTandemCTMismatches[[i]])) {
    plotMismatchPositionFrequencies(sixFourTandemCTMismatches[[i]][[j]],
                                    title = paste("CPD", names(sixFourTandemCTMismatches)[i], 
                                                  names(sixFourTandemCTMismatches[[i]])[j], 
                                                  "Tandem C>T Mismatch Pos"))
  }
}
```
